%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% "computer science"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
% Non-BibTeX users please use
\begin{thebibliography}{99.}
%
% and use \bibitem to create references.
%
%
\bibitem{BatSatKom_2009} Batagelj B (2009) Zapiski predavanj iz predmeta Satelitske komunikacije. UL FE, Ljubljana

\bibitem{VesVreme_2014} Božič J Horvat Ž Kobal C Markovčič L Tešić T (2014)  Vesoljsko vreme. Ladijska elektronika, seminarska naloga, UL FPP, Portorož %8 strani

\bibitem{Girokompas_2012} Brdnik J Krajnc Ž Halilović A Jakopec K Jereb J Feguš M (2012)  Poročilo o prvi kalibraciji kompasa GyroTrac in njegovem preizkusu na jadrnici. Ladijska elektronika, seminarska naloga, UL FPP, Portorož %8 strani

\bibitem{CopRadio_2001} Čop R (2001) Radionavigacija in telematika. UL FPP, Portorož %ISBN 9612360944.

\bibitem{DimcBrcko_2014} Dimc F Brcko T Developing a critical attitude towards the use of GNSS among today`s nautical students. $8^th$ GNSS Conference, The Royal Institute of Navigation, Baška, Hrvaška, 2014. %ISSN 1849-7306.

\bibitem{Groves_2001} Groves P D (2013) Principles of GNSS, Inertial and Multisensor integrated Navigation Systems, 2nd Edition. Artech House, New York %ISBN-13: 978‐1‐60807‐005‐3.

\bibitem{Gyro_Man} Gyrotrac owner's manual, 54-0971 Rev. A. KVH Industries Inc.   %http://www.kvh.com/ViewAttachment.aspx?guidID=%7B8B47298B-AB39-4256-8FB4-4CE405B363D5%7D  %, 84 strani. 

\bibitem{Girokompas_2013} Hrastnik I Kveder U Bevčič M Šušmelj R Stožir Povšnar T Ličina E (2012)  Poročilo o priključitvi in kalibraciji kompasa GyroTrac. Ladijska elektronika, seminarska naloga, UL FPP, Portorož %13 strani

\bibitem{Kostevc_2012} Kostevc D (2012) Navigacijske naprave in sistemi. Izdano v samozaložbi, Ljubljana

\bibitem{GnssSatList_updated} Podatki o satelitih Galileo, Glonass, Beidou in GPS, wikipedia. \\
 \url{https://en.wikipedia.org/wiki/List_of_Galileo_satellites} \\
 \url{https://en.wikipedia.org/wiki/List_of_GLONASS_satellites} \\
 \url{https://en.wikipedia.org/wiki/List_of_Beidou_satellites} \\  \url{https://en.wikipedia.org/wiki/List_of_GPS_satellites} 



% Monographs
%\bibitem{monograph} Kajan E (2002)
%Information technology encyclopedia and acronyms. Springer, Berlin
%Heidelberg New York
% Contributed Works
%\bibitem{contribution} Broy M (2002) Software engineering -- From
%auxiliary to key technologies. In: Broy M, Denert E (eds)
%Software Pioneers. Springer, Berlin Heidelberg New York
% Journal
%\bibitem{journal} Che M, Grellmann W, Seidler S (1997)
%Appl Polym Sci 64:1079--1090
% Theses
%\bibitem{thesis} Ross DW (1977) Lysosomes and storage diseases. MA
%Thesis, Columbia University, New York

\end{thebibliography}
